Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2020-01-08 paper/paper.tex
editing paper.txt...

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{url}
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Journal of Science Education and Technology}
%
\begin{document}

@@

At the University of Silesia, Python is used as a introductory
programming language for students of computer science. There has been
implemented a concept of ``mobile computer classroom'' which consists
of inexpensive and portable thin-client computers which are available
to students in the rental office. They are used to access compute
resources where the required software is available.  Chromebooks
currently play the role of thins clients, which is why all services
must be available through a web browser. Jupyter notebook fits
perfectly in such a scenario. In recent years several scenarios of
teaching workflow based on Juyter notebook have been tested and
implemented.

In the Institute of Physics, the widespread use of the Python-based
computer algebra system SageMath\cite{sagemath} system available in
the browser has been in used for several years. This turned out to be
an excellent solution. The Sage notebook (\texttt{sagenb}) provided
ubiquitous access to computations in science education, and a large
number of teaching materials where produced. This technology was also
replicated in partner high schools as part of the iCSE4school project
(details see \cite{icse4school}). Since 2011, c.a. 2000 students and
over 500 high school pupils have used the system. The Sage notebooks
have been served using a small computer cluster and until today users
have created over 30000 notebook documents.

The notebook system \texttt{sagenb} became obsolete and the currently
SageMath switched to the Jupyter notebook. Additionally, Jupyter
notebook supports using many other programming languages. Therefore en
effort was initiated to replace old \texttt{sagenb} notebooks system
for the sake of Jupyter, and to expand this technology to other
teaching programmes.

In this paper, we will mainly concentrate on the case of course
``Introduction to Artificial Intelligence``, which is attended by
c.a. 50 Applied Computer Science students every year. The course uses
Jupyter notebook as a teaching tool during both the lectures and
tutorials. Students had to submit their work in the form of notebooks
using \texttt{nbgrader} software. All excercices include automated
tests to help both students as well as teachers.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figs/notebook.png}
\caption{Jupyter notebooks is a executable document which contains
  rich-text and code (e.g. in Pyton). }
\label{fig:notebook}
\end{figure}

@@

Jupyterhub a software providing a way to serve Jupyter notebook for
multiple users. It can be used in a single classes of students, or can
be deployed centrally on a faculty level. In both cases it provides
computational resources to run a Jupyter notebook from a remote
computing center. It can be used to distribute problem sets or more
generally teaching material easily. and without the need for a local
Python installation. Furthermore, this approach ensures a consistent
working environment for all students.

@@

\section{\texttt{nbgrader}}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{url}
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Journal of Science Education and Technology}
%

\hyphenation{Ju-py-ter} 
\begin{document}

@@

At the University of Silesia, Python is used as a introductory
programming language for undegraduate students of ``Applied Computer
Science'' programme. There has been implemented a concept of ``mobile
computer classroom'' which consists of inexpensive and portable
thin-client computers which are available to students in the rental
office. They are used to access compute resources where the required
software is available.  Chromebooks currently play the role of thins
clients, which is why all services must be available through a web
browser. Jupyter notebook fits perfectly in such a scenario. In recent
years several teaching workflows based on Juyter notebook have been
tested and implemented.

At the Institute of Physics, the Jupyter notebook is not the first
teaching experience with web based software for mathamatical
explorations. SageMath\cite{sagemath}, the Python-based computer
algebra system has been served to students and academic teachers for
several years. The Sage notebook (\texttt{sagenb}) provided ubiquitous
access to computations in science education, and a large number of
teaching materials where produced. This technology was also replicated
in partner high schools as part of the iCSE4school project (details
see \cite{icse4school}). Since 2011, c.a. 2000 students and over 500
high school pupils have used the system. The Sage notebooks have been
served using a small computer cluster and until today users have
created over 30000 notebook documents.  Over time, the notebook system
\texttt{sagenb} has become obsolete and the currently SageMath
software is available as a kernel to the Jupyter notebook. Therefore
en effort was initiated to replace old \texttt{sagenb} notebooks
system for the sake of Jupyter, and to expand this technology to other
teaching programmes.

In this paper, we will the course: ``Introduction to Artificial
Intelligence``, which is attended by c.a. 50 Applied Computer Science
students every year. The course uses Jupyter notebook as a main
teaching tool during both the lectures and tutorials. All materials
are discributed and collected in as \texttt{*.ipynb} file. Moreover,
students submit their assignments \texttt{nbgrader} software installed
on publicly available web-address. All excercices include automated
tests to help both students in self assessment as well as teachers in
grading.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figs/notebook.png}
\caption{Jupyter notebooks is a executable document which contains
  rich-text and code (e.g. in Python, R). }
\label{fig:notebook}
\end{figure}

@@

Jupyterhub a software providing a way to serve Jupyter notebook for
multiple users. It can be used in a single classes of students, or can
be deployed centrally on a faculty level. In both cases it provides
computational resources to run a Jupyter notebook from a remote
computing center. It can be used to distribute problem sets or more
generally teaching material easily and without the need for a local
Python installation. Furthermore, this approach ensures a consistent
working environment for all students.

@@

\section{Creating and Grading assignments with \texttt{nbgrader}}

@@

\section{Typical workflow with Jupyter and nbgrader}

\subsection{Subnotebooks }

\subsection{In Lecture hand out  Perpectron-quizz}

Jupyter notebook is used as hand-out material given during the lecture on learning Perceptron

# Layered neural network

\section{Evaluation}
